From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-20 Pi+/paper/finite.tex
Normalisation lemmas

18. We define the equivalence classes on List (Fin n) to be precisely these
elements that have the same normal form.

>>>>

By strong normalisation, we get a unique choice function that produces a normal form for terms of $\List[\Fin[n]]$.
Equivalence classes on $\List[\Fin[n]]$ are precisely those terms that have the same normal form.
